### 2005-11-21 doc/EFA/efa.tex
*** empty log message ***

Given an extended finite automaton $A=\langle Q, \Sigma, \delta,
q_i, Q_m, X, G ,x_0, X_m \rangle$ with simple guard and action
functions, the algorithm can be divided into four steps:\\
- Form a regular FA, $A'$, from $A$ by removing $G$, $X$, $X_m$,
$x_0$ and change the names of all enabled events $\sigma$ to
$q\sigma$ i.e. the associate them with the corresponding
transition.\\
- Rename the events $q\sigma$ in $A'$ further into $|g_{q \sigma}|$ identical transitions with event names: $\{(q\sigma)_k\}^{|g_{q \sigma}|}_{k=1}$.\\
- Realize an automata $A_{x_k}$ for each variable $x_k$, with
marked "states" $X_{mk}$, initial state $x_{k 0}$ and with as many events the total number of events in $A'$.
The transitions correspond to the action functions and they are enabled if the guard formula is true.\\
- Synchronize all automata $A_{x_k}$, $k=1,...,n$ and $A'$.\\
- Change back to original event names.
\newpage
\subsection{Synchronous composition of EFA's with common variables}

>>>>

Given an extended finite automaton $A=\langle Q, \Sigma, \delta,
q_i, Q_m, X, G ,x_0, X_m \rangle$ with simple guard and action
functions, the algorithm can be divided into four steps:\\
- Form a regular FA, $A'$, from $A$ by removing $G$, $X$, $X_m$,
$x_0$ and change the names of all enabled events $\sigma$ to
$q\sigma$ i.e. the associate them with the corresponding
transition.\\
- Rename the events $q\sigma$ in $A'$ further into $|g_{q \sigma}|$ identical transitions with event names: $\{(q\sigma)_k\}^{|g_{q \sigma}|}_{k=1}$.\\
- Realize an automata $A_{x_k}$ for each variable $x_k$, with
marked "states" $X_{mk}$, initial state $x_{k 0}$ and with as many events the total number of events in $A'$.
The transitions correspond to the action functions and they are enabled if the guard formula is true.\\
- Synchronize all automata $A_{x_k}$, $k=1,...,n$ and $A'$.\\
- Change back to original event names.
\newpage
\subsection{Translating hierarchical structures to EFA's}
It is well known that hierarchical structures of states and
transitions reduce the descriptive complexity of automata models.
We shall in this section show how the hierarchy in state charts
can be translated into EFA's.

In what follows, states are represented by boxes and hierarchy is
illustrated by being inside or outside the boxes. Arrows between
states represents transitions and are labelled with the lower case
Greek letters, $\alpha$-$\omega$. An arrow that leaves a box
applies to all sub-states inside the box. The common way to enter
a group of states its by the system's history in that group. The
simplest way of doing this is to enter the most recently visited
state in the group. Hierarchical structures with quite general
history functions can easily be translated into EFA's.

\subsection{Synchronous composition of EFA's with common variables}
